\documentclass{template} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nikita Podelenko} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(626) 394-67-46 \\ Los Angeles, CA (open to remote, relocate)} 
\address{\href{mailto:n.podelenko@gmail.com}{n.podelenko@gmail.com} \\ \href{https://linkedin.com/in/nikita39}{linkedin.com/in/nikita39} \\ \href{podelenko.pro}{podelenko.pro}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Full Stack Engineer with over 10 years of experience specializing in JavaScript, TypeScript, Vue/Nuxt, React/Next, Node.js. Proven track record of increasing company profits by over \$500K through high-quality code and technology strategies. Looking for a challenging Software Engineer role to leverage my skills and contribute to business growth through technology. Big fan of new space, EV enthusiast.}


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & TypeScript, JavaScript, React, Next, Vue, Nuxt, Python, AI, Langchain\\ 
 & Tailwind, Node.js, Express, Fastify, NestJS, REST APIs, GraphQL \\
Databases \& Cloud & PostgreSQL, MySQL, MongoDB, AWS, GCP, Kubernetes, Docker\\
Soft Skills & Agile, Problem-solving, Teamwork, Communication, Openness to criticism\\
Business \& Marketing Skills: & Establishing communication between business \& developers\\
Hobby & Neural Networks, GPT, Cryptocurrency, Rocket Launches, Hiking, EV\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Fullstack Senior Developer} \hfill Sept 2015 --- Present\\
ONMoon LLC \hfill \textit{Remote}

\begin{minipage}{0.95\textwidth}
 \begin{itemize}
    \vspace{0.1cm}
    \itemsep 1pt {} 
    \item \textbf{Fullstack} For latest 8 years I've beeing creating and managing projects for gambling industry on all stages of development, from MVP to production. I've been working with all types of projects, from small teams to big companies with 100+ employees.
    \item \textbf{Legacy code maintenance} Led engineering of high-loaded gambling projects, resulting in 60\% increase in user
    engagement by transforming legacy PHP project into scalable, high performance multi-project engine.
    \item \textbf{Managment, Leadership} Developed Skinpay.com, an innovative platform for instant selling of in-game skins with immediate payment receipt, leading to 40\% upsurge in revenue.
    \item \textbf{Payment processing} Built robust payment system that processed over 1 million transactions and integrated seamlessly with 30 different partner APIs.
    \item \textbf{DevOps} Successfully transitioned entire project from dedicated servers to Google Cloud, including databases and instances, demonstrating proficiency in cloud technologies like AWS and Google Cloud.
    \item \textbf{Highload} Contributed significantly to core backend infrastructure of Steam Inventory Helper project serving 1M+ users by developing internal and external APIs.
    \item \textbf{Achivements} Developed and launched 10+ projects, including 3 high-load projects, 2 of which brought in more than \$1 million for the company.
 \end{itemize}
\end{minipage}

\vspace{0.5cm}

\textbf{Fullstack Developer} \hfill Jun 2021 --- Jun 2022\\
iGambling Development (OnMoon Subdivision) \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item As product owner and developer, dedicated a year to build project and sold it.
     \item Architected and developed an full stack MVP iGambling project single-handedly, utilizing JS/TS microservices
     \item Build project a template for microservices using TypeScript, Google Cloud Pubsub for microservice,\\and PostgreSQL, resulting in improved development efficiency and development speed by 40\%
     \item Developed 10+ unique games using JavaScript/TypeScript, integrated 6000+ partner-provided games via API collaboration, enhancing platform diversity and user engagement.
     \item Integrated over 10+ payment systems and two blockchains (web3 deposits, metamask) into platform, enhancing transaction capabilities and user experience.
     \item Led interviewing and selection process for initial 5-member project team post-production launch, contributing to successful project execution.
     \item Engineered affiliate network platform utilizing Nuxt/Vue, resulting in over 100 partners joining within first few months, boosting company's partner base.
 \end{itemize}
%\pagebreak
 \textbf{Fullstack Developer} \hfill Oct 2014 --- Sept 2015\\
MDK (Now MAIN Community) \hfill \textit{Moscow, Russia}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Developed features for a Russian Social Media with 3M+ subscribers using PHP, JavaScript and Python, leading to growth up to 10\% in user engagement.
     \item Solely managed LAMP stack for gaming projects, developed SaaS tool reducing spam comments on VK social networks (like Facebook), resulting in 90\% reduction in spam comments.
     \item Engineered fullstack (frontend and backend) for pioneering CS:GO jackpot website utilizing Steam API, facilitating first-ever in-game skin gambling
 \end{itemize}

 \textbf{Fullstack Developer} \hfill Dec 2012 --- Sept 2014\\
 Twite.Ru / VideoSeed / AdPro \hfill \textit{Saint Petersburg, Russia}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Utilized LAMP Stack in developing high-traffic web application, improving server response time by 30\%.
     \item Engineered monetization feature for social media users using PHP, leading to 20\% increase in user engagement.
     \item Developed a big number of admin panels featuring statistics and caching capabilities, handling large datasets for first time, resulting in improved data management and efficiency
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Networks}, Immanuel Kant Baltic Federal University \hfill {2009 - 2015} \vspace{0.2cm}\\
Immanuel Kant Baltic Federal University is the largest educational, scientific, and cultural center in the westernmost region of Russia. IKBFU is one of the 10 Russian federal universities and it holds a leading position in education and science in the Northwestern Federal District.
Top-1 univercity of Kaliningrad and Top-30 of Russia \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{GPTaskBot} {A revolutionary chatbot powered by cutting-edge technology that can answer any question and perform any task inside Telegram \href{https://gptask.io/}{(Try it here)}.
    \begin{itemize}
        \itemsep -3pt {} 
        \item Developed chatbot to improve user engagement on Telegram, using GPT-4, Google Cloud, and Telegram APIs.
        \item Task was to create bot capable of voice message recognition, group chat compatibility, and image generation based on descriptions.
        \item Developed this in TypeScript and hosted it on Google Cloud Platform (GCP). The bot was integrated seamlessly into Telegram.
        \item Bot serves over \textbf{100k} messages daily and has gained \textbf{40,000} users and more than \textbf{2000 paid} subscribers.
    \end{itemize}
}
\item \textbf{Voice2Calendar} {Again, a Telegram bot that allows you to add events to your Google Calendar by voice.
    \begin{itemize}
        \itemsep -3pt {} 
        \item Developed in TypeScript and hosted on Google Cloud Functions, using Whisper, Langchain, and Google Calendar APIs.
        \item Chatbot using langchain to extract event information from messages, use search engine to find event location and add event to Google Calendar
        \item Has a paid subscription model with free option
    \end{itemize}
}
Check out my small-fun projects on \href{https://podelenko.pro/#fun}{podelenko.pro}
\end{rSection} 


%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Admin for the local Tesla commnunity with over 200+ memebers. Actively involved in facilitating offline and online events, including meetups, test drives, and other activities.
\end{itemize}


\end{rSection}


\end{document}
